Roster Review (Generic)

### 2019-05-06 rosterReview_generic.Rmd
More projections, updated data

proj_batter <- add_z_scores_to_projections("data/depthChartProjections_ros_batters_20190429.csv","batter") 
proj_pitcher <- add_z_scores_to_projections("data/depthChartProjections_ros_pitchers_20190429.csv", "pitcher")

@@

```{r}
rosters_with_adj_projections %>% 
  filter(!grepl("Free Agent",team),
         # grepl("SP|3B",display_position)
         ) %>% 
  ggplot(aes(x=team,y=zar,color=type)) +
  geom_boxplot() +
  # geom_jitter(aes(text=name_full), width = .2) +
  coord_flip() -> tb

>>>>

proj_batter <- add_z_scores_to_projections("data/depthChartProjections_ros_batters_20190506.csv","batter") 
proj_pitcher <- add_z_scores_to_projections("data/depthChartProjections_ros_pitchers_20190506.csv", "pitcher")

@@

```{r}
rosters_with_adj_projections %>% 
  #filter(!grepl("Free Agent",team),
         # grepl("SP|3B",display_position)
   #      ) %>% 
  ggplot(aes(x=team,y=zar,color=type)) +
  geom_boxplot() +
  # geom_jitter(aes(text=name_full), width = .2) +
  coord_flip() -> tb
